CHEC Study Sweat Chloride

### 2025-07-29 Edith Zemanick/Sweat Variability/sweat_test_analysis_chec.qmd
small formatting changes

```{r}
ggplot(chec_long, aes(x = pre_post, y = ratio)) +
  geom_boxplot() +
  geom_signif(
    comparison = list(c("Pre-Modulator", "Post-Modulator")),
    test = "wilcox.test", test.args = list(paired = TRUE, exact = FALSE),
    y_position = 3.5, map_signif_level = function(p) 
      format.pval(p, digits = 3, eps = 0.001)
  ) +
  theme_bw() +
  theme(legend.title = element_blank(), axis.title.x = element_blank()) +
  ylab("Na:Cl Ratio") +
  facet_wrap(~modqual)
```

@@

```{r}
model_df <- chec_long %>%
  select(subject, cl, na, ratio, pre_post) %>%
  drop_na()
model_df$cl = model_df$cl / 10
model_df$na = model_df$na / 10
# From Amalia
m1 <- glm(pre_post ~ cl, data = model_df, family = "binomial")
m2 <- glm(pre_post ~ cl + na, data = model_df, family = "binomial")
m3 <- glm(pre_post ~ cl * na, data = model_df, family = "binomial")
m4 <- glm(pre_post ~ scale(ratio), data = model_df, family = "binomial")
gt(compare_performance(m1, m2, m3, m4, metrics = "common")) %>%
  fmt_number(decimals = 3)
model_df$m1_pred <- factor(predict(m1, type = "response") > 0.5,
  levels = c(F, T), labels = c("pred_pre", "pred_post")
)
model_df$m2_pred <- factor(predict(m2, type = "response") > 0.5,
  levels = c(F, T), labels = c("pred_pre", "pred_post")
)
model_df$m3_pred <- factor(predict(m3, type = "response") > 0.5,
  levels = c(F, T), labels = c("pred_pre", "pred_post")
)
model_df$m4_pred <- factor(predict(m4, type = "response") > 0.5,
  levels = c(F, T), labels = c("pred_pre", "pred_post")
)
# Tim's model
tm <- lmer(cl ~ pre_post * na + (1 | subject), data = model_df)
```

>>>>

```{r}
ggplot(chec_long, aes(x = pre_post, y = ratio)) +
  geom_boxplot() +
  geom_signif(
    comparison = list(c("Pre-Modulator", "Post-Modulator")),
    test = "wilcox.test", test.args = list(paired = TRUE, exact = FALSE),
    y_position = 3.5, map_signif_level = function(p) {
      format.pval(p, digits = 3, eps = 0.001)
    }
  ) +
  theme_bw() +
  theme(legend.title = element_blank(), axis.title.x = element_blank()) +
  ylab("Na:Cl Ratio") +
  facet_wrap(~modqual)
```

@@

```{r}
model_df <- chec_long %>%
  select(subject, cl, na, ratio, pre_post) %>%
  drop_na()
model_df$cl <- model_df$cl / 10
model_df$na <- model_df$na / 10
# From Amalia
m1 <- glm(pre_post ~ cl, data = model_df, family = "binomial")
m2 <- glm(pre_post ~ cl + na, data = model_df, family = "binomial")
m3 <- glm(pre_post ~ cl * na, data = model_df, family = "binomial")
m4 <- glm(pre_post ~ scale(ratio), data = model_df, family = "binomial")
gt(compare_performance(m1, m2, m3, m4, metrics = "common")) %>%
  fmt_number(decimals = 3)
model_df$m1_pred <- factor(predict(m1, type = "response") > 0.5,
  levels = c(F, T), labels = c("pred_pre", "pred_post")
)
model_df$m2_pred <- factor(predict(m2, type = "response") > 0.5,
  levels = c(F, T), labels = c("pred_pre", "pred_post")
)
model_df$m3_pred <- factor(predict(m3, type = "response") > 0.5,
  levels = c(F, T), labels = c("pred_pre", "pred_post")
)
model_df$m4_pred <- factor(predict(m4, type = "response") > 0.5,
  levels = c(F, T), labels = c("pred_pre", "pred_post")
)
# Tim's model
tm <- lmer(cl ~ pre_post * na + (1 | subject), data = model_df)
```
